### 2023-09-27 accepted/COPSolver/manuscript.tex
updating paper

\noindent
\textbf{combinatorial optimization problem; exact method; multi-product batch problem; processing time maximization.}\\
\vskip0.5cm
\newpage
\noindent
\textbf{Code metadata}\\

@@

Some industrial equipment process a set of jobs (batches) simultaneously. For production scheduling in these equipment, in addition to the sequencing and determination of the batches sizes, it is also necessary to define the set of batches that will be processed simultaneously in each time interval. These compound batches are called p-batch (parallel batching). Since most of p-batch problems are NP-Hard, many scientific works propose different local search heuristics for solving these problems (Fowler and Mönch, 2022). When applying some local search heuristics for solving a p-batch problem, it becomes necessary to determine the maximum p-batch processing time at each iteration. So, the method applied to solve this sub-problem can have a strong impact on the computational cost of the local search algorithm proposed for solving p-batch problems. As reported earlier, COPSolver's library for solving the multi-product p-batch processing time maximization problem has an application of the Fraga's method to solve this sub-problem, which has very low computational cost. Therefore, this library can be used to implement local search heuristics-based algorithms developed for solving p-batch problems, generating a high impact on the efficiency of these algorithms. An article has been submitted for publication, which present the exact method proposed for solving multi-product p-batch processing time maximization problems as well as an extensive study on the computational efficiency of the COPSolver\_1.0-1 (Fraga \emph{et al.}, 2023). In order to make this software available to the rest of the world, all the necessary files that is required to compile and run the software successfully have been published to the codeocean project (Fraga, 2023).

>>>>

\noindent
\textbf{combinatorial optimization problem; exact method; p-batch problem; processing time maximization.}\\
\vskip0.5cm
\newpage
\noindent
\textbf{Code metadata}\\

@@

Some industrial equipment process a set of jobs (batches) simultaneously. For production scheduling in these equipment, in addition to the sequencing and determination of the batches sizes, it is also necessary to define the set of batches that will be processed simultaneously in each time interval. These compound batches are called p-batch (parallel batching). Since most of p-batch problems are NP-Hard, many scientific works propose different local search heuristics for solving these problems (Fowler and Mönch, 2022). When applying some local search heuristics for solving a p-batch problem, it becomes necessary to determine the maximum p-batch processing time at each iteration. So, the method applied to solve this subproblem can have a strong impact on the computational cost of the local search algorithm proposed for solving p-batch problems. As reported earlier, COPSolver's library for solving the multi-product p-batch processing time maximization problem has an application of the Fraga's method to solve this subproblem, which has very low computational cost. Therefore, this library can be used to implement local search heuristics-based algorithms developed for solving p-batch problems, generating a high impact on the efficiency of these algorithms. An article has been submitted for publication, which present the exact method proposed for solving multi-product p-batch processing time maximization problems as well as an extensive study on the computational efficiency of the COPSolver\_1.0-1 (Fraga \emph{et al.}, 2023). In order to make this software available to the rest of the world, all the necessary files that is required to compile and run the software successfully have been published to the codeocean project (Fraga, 2023).
